---
title: "Soccer Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1872-2022 International Soccer Game Results Analysis

I create three questions I am interested and try to figure out.

```{r}
goalscorers <- read.csv("C:/Users/russe/Downloads/goalscorers.csv")
results <- read.csv("C:/Users/russe/Downloads/results.csv")
shootouts <- read.csv("C:/Users/russe/Downloads/shootouts.csv")
```


#Question 1 
Which minutes have most goals during a regular time of a soccer game?

```{r cars}
total_goals <- sum(results$home_score) + sum(results$away_score)
print(total_goals)
library(dplyr)
goal_summary <- goalscorers %>%
  filter(minute >= 0 & minute <= 90) %>%
  group_by(minute) %>%
  summarise(total_goals = n()) %>%
  arrange(-total_goals)
top_minute <- goal_summary[1, ]
print(top_minute)

goal_summary_least <- goalscorers %>%
  filter(minute >= 0 & minute <= 90) %>%
  group_by(minute) %>%
  summarise(total_goals = n()) %>%
  arrange(total_goals)
bottom_minute <- goal_summary_least[1, ]
print(bottom_minute)

library(ggplot2)
game_goal <- ggplot(goal_summary, aes(x=minute, y=total_goals)) +
  geom_line() +
  labs(title="Goals Scored Per Minute",
       x="Minute",
       y="Number of Goals") +
  theme_minimal()
game_goal + scale_x_continuous(breaks = c(0, 30, 60, 90))
```
After run these code, I found in soccer matches, the most goals are scored in the 90th minute, the last minute of the game! There are many last-minute winners! And also, I found the least minutes happens on first minutes. And I graph a line graph to show the frequency of goals per minutes.

# Question 2
Which country has the most dominance over another country, and which two countries are the friendliest?

```{r pressure, echo=FALSE}
results <- results %>%
  mutate(results = case_when(
    home_score > away_score ~ "Home Win",
    home_score < away_score ~ "Away Win",
    TRUE ~ "Draw"))
match_summary <- results %>%
  group_by(home_team, away_team, results) %>%
  summarise(count = n(), .groups = "drop")
top_win <- match_summary %>%
  filter(results != "Draw") %>%
  arrange(-count) %>%
  head(1)
top_draw <- match_summary %>%
  filter(results == "Draw") %>%
  arrange(-count) %>%
  head(1)
top_away_win <- match_summary %>%
  filter(results == "Away Win") %>%
  arrange(-count) %>%
  head(1)

print(top_win)
print(top_draw)
print(top_away_win)
```

Question 2, I want to figure out during 150 years, which country win another country most times, I called it 'most dominance country' and which two countries have draw most times, I called them 'most friendly countries'. After I use the r code to check, I found Argentina win Uruguay 62 times during 150 years, and Kenya and Uganda draw 24 times, they are so friendly. After I did these work, I want to which country have win most on away to a home country to made the home field silence. And the interesting things I found that England have won 35 times away from Northern Ireland. And these two countries both belong to United Kingdom, but they are not friends, they have many conflicts in history.

# Question 3
Which city host most international games?
```{r}
library(dplyr)
library(leaflet)
library(maps)
library(ggplot2)

world_cities <- as.data.frame(maps::world.cities)
unique_cities <- data.frame(city = unique(results$city))
city_coords <- semi_join(world_cities, unique_cities, by = c("name" = "city"))
city_summary <- results %>%
  group_by(city, country) %>%
  summarise(count = n(), .groups = "drop")
city_summary <- left_join(city_summary, city_coords, by = c("city" = "name", "country" = "country.etc"))
na_rows <- which(is.na(city_summary$lat) | is.na(city_summary$long))
if (length(na_rows) > 0) {
  print(city_summary[na_rows, ])
}
# m <- leaflet(city_summary) %>%
#   addTiles() %>%
#   addCircleMarkers(
#     ~long, ~lat, 
#     radius = ~count/100,  
#     color = "#1E90FF",  
#     fillColor = "#1E90FF",
#     fillOpacity = 0.5,  
#     weight = 1,  
#     opacity = 1,  
#     label = ~paste(city, ":", count, "games"),
#     popup = ~paste(city, ":", count, "games")
#   )
# 
# m

city_summary <- results %>%
  group_by(city) %>%
  summarise(count = n(), .groups = "drop")

top_cities_all <- city_summary %>%
  arrange(-count) %>%
  head(10) 

ggplot(top_cities_all, aes(x = reorder(city, -count), y = count)) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = count), position = position_dodge(width = 0.9), hjust = -0.3) +
  coord_flip() +
  labs(title = "Top 10 Cities with Most Matches Overall",
       x = "City",
       y = "Number of Matches") +
  theme_minimal()
```

In the Final Question, I want to find which city host most international games, which I will call this city as 'Favorite soccer city'. First, I try to use world map and use circle size to show. However, I found there so many cities have host international games, and I cannot found which city is the top. So I use bar graph to instead. And the result surprised me. Because from my idea, I think this city must be European city. However, the first cities to host international games are all Asian cities.
